`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`

### 2020-06-18 analysis/VOCC/3-vocc-dist.Rmd
run vocc with updated climate est

#### TRIM environment to range sampled
```{r}
nd_all <- readRDS(paste0("data/predicted-DO-new.rds")) %>% select(X, Y, year, temp, do_est)
fishing <- readRDS("data/_fishing_effort/fishing-effort-grid.rds")
# fishing <- readRDS("data/fishing-effort-grid-6hr.rds")

@@

```{r eval = F}
effort <- plot_vocc(gf,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  # NA_label = "NA",
  fill_col = "squashed_effort",
  fill_label = "mean effort",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  # high_fill = "Steel Blue 4",
  # low_fill = "Red 3",
  # white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = fourth_root_power #
) + labs(
  title = "Fishing presssure",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

fish_t <- plot_vocc(gf,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  # NA_label = "NA",
  fill_col = "fishing_trend",
  fill_label = "trend in fishing effort",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  # high_fill = "Steel Blue 4",
  # low_fill = "Red 3",
  # white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = sqrt # no_trans #
) + labs(
  title = "Fishing presssure",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

```{r eval=F}
plot_vocc(gf2,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "dvocc",
  fill_label = "temperature \ndvocc",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power # sqrt #
) + labs(
  title = "distance-based temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year), " min temp SD = ", signif(temp_min_sd, 2), " x 2 for 95% min threshold of change")
)
```

@@

plot_vocc(gf2,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "squashed_velocity",
  fill_label = "temperature \nvelocity",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power # sqrt #
) + labs(
  title = "gradient-based temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)
```

```{r eval=F}
grad2 <- plot_vocc(gf2,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "temperature \ntrend",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # log10 # fourth_root_power # sqrt #
) + labs(
  title = "temp trend",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

```{r eval=F}
grad0dv <- plot_vocc(gf0,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "dvocc",
  fill_label = "DO and temp \ndvocc",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power # sqrt #
) + labs(
  title = "distance-based DO and temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year), " DO SD = ", signif(do_sd_choice, 2), " x 2 for threshold for do change")
)

@@

grad0v <- plot_vocc(gf0,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "squashed_velocity",
  fill_label = "DO velocity",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power
) + labs(
  title = "do velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

```{r eval=F}
grad0 <- plot_vocc(gf0,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "DO trend",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans #
) + labs(
  title = "do trend",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

```{r eval=T}
gradbv <- plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "dvocc",
  fill_label = "km/decade",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  mid_fill = "lightyellow",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power # sqrt #
) + labs(
  title = paste0(species, " (", age, ") distance-based biotic velocity"),
  subtitle = paste0(min(d$year), "-", max(d$year), " threshold for change = ", b_choice, "")
)

@@

grad3 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "squashed_velocity",
  fill_label = "biotic \nvelocity",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
   mid_fill = "lightyellow",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt # no_trans #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biotic velocity ", min(d$year), "-", max(d$year))
)
grad3
```

@@

grad3 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "gradient",
  fill_label = "biotic \ngradient",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt # no_trans #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biotic gradient for final year")
)
grad3
```

```{r eval=T}
#raster_max <- quantile(gf3$mean_biomass, 0.995, na.rm = T)
gf3$mean_biomass2 <- collapse_outliers(gf3$mean_biomass, c(0, 0.995))
grad4 <- gfranges::plot_vocc(gf3,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "mean_biomass2",
  fill_label = "mean",
  raster_alpha = 1,
 # raster_limits = c(0, raster_max),
  na_colour = "white",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Mean biomass ", min(d$year), "-", max(d$year))
)
grad4
```

```{r eval=T}
grad5 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "biomass \ntrend",
  raster_alpha = 1,
  # raster_limits = c(0, 10),
  na_colour = "black",
  white_zero = TRUE,
   mid_fill = "lightyellow",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biomass trend ", min(d$year), "-", max(d$year))
)
grad5
```

```{r eval=T}
grad6 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "cv",
  fill_label = "sd in log space",
  raster_alpha = 1,
  # raster_limits = c(0, 7),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biotic variability (cv from vocc_gradient_calc) ", min(d$year), "-", max(d$year))
)
grad6
```

```{r eval=F}
raster_max <- quantile(gf3t$CV, 0.90, na.rm = TRUE)
grad7 <- gfranges::plot_vocc(gf3t,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "CV",
  fill_label = "CV",
  raster_alpha = 1,
  raster_limits = c(0, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("CV in estimated biomass ", min(d$year), "-", max(d$year))
)
grad7
```

@@

write.csv(vocc, file = paste0(
  "data/_dvocc_", age, "/", age, "-w-do-nulls-", spp, "-", ssid_string, covs, "-", min(d$year), "-", max(d$year), ".csv"
))

@@

```{r}
vocc  <- read.csv(paste0(
  "data/_dvocc_", age, "/", age, "-w-do-nulls-", spp, "-", ssid_string, "-", covs, "-", min(d$year), "-", max(d$year), ".csv"
))
vocc_t <- filter(vocc, mean_biomass > lower_density_threshold)
```

>>>>

#### TRIM environment to range sampled
```{r}
nd_all <- readRDS(paste0("data/predicted-DO-june-2020.rds")) %>% select(X, Y, year, temp, do_est)
fishing <- readRDS("data/_fishing_effort/fishing-effort-grid.rds")
# fishing <- readRDS("data/fishing-effort-grid-6hr.rds")

@@

```{r eval = F}
effort <- plot_vocc(gf,
  raster_cell_size = 4,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  # NA_label = "NA",
  fill_col = "squashed_effort",
  fill_label = "mean effort",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  # high_fill = "Steel Blue 4",
  # low_fill = "Red 3",
  # white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = fourth_root_power #
) + labs(
  title = "Fishing presssure",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

fish_t <- plot_vocc(gf,
  raster_cell_size = 4,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  # NA_label = "NA",
  fill_col = "fishing_trend",
  fill_label = "trend in fishing effort",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  # high_fill = "Steel Blue 4",
  # low_fill = "Red 3",
  # white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = sqrt # no_trans #
) + labs(
  title = "Fishing presssure",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

```{r eval=F}
plot_vocc(gf2,
  # theme = "black",
  raster_cell_size = 4,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "dvocc",
  fill_label = "temperature \ndvocc",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power # sqrt #
) + labs(
  title = "distance-based temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year), " min temp SD = ", signif(temp_min_sd, 2), " x 2 for 95% min threshold of change")
)
```

@@

plot_vocc(gf2,
  # theme = "black",
  raster_cell_size = 4,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "squashed_velocity",
  fill_label = "temperature \nvelocity",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power # sqrt #
) + labs(
  title = "gradient-based temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)
```

```{r eval=F}
grad2 <- plot_vocc(gf2,
  raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "temperature \ntrend",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # log10 # fourth_root_power # sqrt #
) + labs(
  title = "temp trend",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

```{r eval=F}
grad0dv <- plot_vocc(gf0,
  raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "dvocc",
  fill_label = "DO and temp \ndvocc",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power # sqrt #
) + labs(
  title = "distance-based DO and temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year), " DO SD = ", signif(do_sd_choice, 2), " x 2 for threshold for do change")
)

@@

grad0v <- plot_vocc(gf0,
  raster_cell_size = 4,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "squashed_velocity",
  fill_label = "DO velocity",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power
) + labs(
  title = "do velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

```{r eval=F}
grad0 <- plot_vocc(gf0,
  raster_cell_size = 4,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "DO trend",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans #
) + labs(
  title = "do trend",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

```{r eval=T}
gradbv <- plot_vocc(gf3t,
  raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "dvocc",
  fill_label = "km/decade",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  mid_fill = "lightyellow",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = no_trans # fourth_root_power # sqrt #
) + labs(
  title = paste0(species, " (", age, ") distance-based biotic velocity"),
  subtitle = paste0(min(d$year), "-", max(d$year), " threshold for change = ", b_choice, "")
)

@@

grad3 <- gfranges::plot_vocc(gf3t,
  raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "squashed_velocity",
  fill_label = "biotic \nvelocity",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
   mid_fill = "lightyellow",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt # no_trans #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biotic velocity ", min(d$year), "-", max(d$year))
)
grad3
```

@@

grad3 <- gfranges::plot_vocc(gf3t,
  raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "gradient",
  fill_label = "biotic \ngradient",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt # no_trans #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biotic gradient for final year")
)
grad3
```

```{r eval=T}
#raster_max <- quantile(gf3$mean_biomass, 0.995, na.rm = T)
gf3$mean_biomass2 <- collapse_outliers(gf3$mean_biomass, c(0, 0.995))
grad4 <- gfranges::plot_vocc(gf3,
  raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "mean_biomass2",
  fill_label = "mean",
  raster_alpha = 1,
 # raster_limits = c(0, raster_max),
  na_colour = "white",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Mean biomass ", min(d$year), "-", max(d$year))
)
grad4
```

```{r eval=T}
grad5 <- gfranges::plot_vocc(gf3t,
  raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "biomass \ntrend",
  raster_alpha = 1,
  # raster_limits = c(0, 10),
  na_colour = "black",
  white_zero = TRUE,
   mid_fill = "lightyellow",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biomass trend ", min(d$year), "-", max(d$year))
)
grad5
```

```{r eval=T}
grad6 <- gfranges::plot_vocc(gf3t,
  raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "cv",
  fill_label = "sd in log space",
  raster_alpha = 1,
  # raster_limits = c(0, 7),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("Biotic variability (cv from vocc_gradient_calc) ", min(d$year), "-", max(d$year))
)
grad6
```

```{r eval=F}
raster_max <- quantile(gf3t$CV, 0.90, na.rm = TRUE)
grad7 <- gfranges::plot_vocc(gf3t,
  raster_cell_size = 4,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "CV",
  fill_label = "CV",
  raster_alpha = 1,
  raster_limits = c(0, raster_max),
  na_colour = "black",
  # white_zero = TRUE,
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  axis_lables = FALSE,
  transform_col = sqrt #
) + labs(
  title = paste0(species, " (", age, ")"), #
  subtitle = paste0("CV in estimated biomass ", min(d$year), "-", max(d$year))
)
grad7
```

@@

write.csv(vocc, file = paste0(
  "data/_newclim_", age, "/", age, "-w-do-nulls-", spp, "-", ssid_string, covs, "-", min(d$year), "-", max(d$year), ".csv"
))

@@

```{r}
vocc  <- read.csv(paste0(
  "data/_newclim_", age, "/", age, "-w-do-nulls-", spp, "-", ssid_string, covs, "-", min(d$year), "-", max(d$year), ".csv"
))
vocc_t <- filter(vocc, mean_biomass > lower_density_threshold)
```
